R-LIME: LIME法における矩形制約と最適化

### 2024-04-10 paper/paper.tex
modify abstract of paper

\ifnum\mode=0
  \pagestyle{plain}
  \pagenumbering{roman}
  \tableofcontents
  \newpage
  \listoffigures\listoftables\clearpage
  \AddToHook{cmd/section/before}{\clearpage}
  \pagestyle{plain}
  \pagenumbering{arabic}
\else
  % The abstract should briefly summarize the contents of the paper in
  % 150--250 words.
  \begin{abstract}
    In recent years,
    complex machine learning models have been introduced
    in various industrial fields due to their high accuracy.
    However,
    their complexity has been a major obstacle to implementation
    in sensitive decision-making situations.
    In order to address this problem,
    various post-hoc explanation methods have been proposed,
    but they have not been able to achieve interpretability of
    both the explanation and its scope.
    We propose a new method, R-LIME,
    which interprets a complex classifier in an interpretable scope.
    R-LIME locally approximates a decision boundary of a black-box classifier
    in a rectangular region
    and maximizes the region as long as the accuracy of the linear
    classifier is higher than a given threshold.
    The resulting rectangular region is interpretable for users because it is
    expressed as a conjunction of feature predicates.
    We demonstrate the effectiveness of the proposed method through
    qualitative and quantitative comparisons with the existing method
    using a real-world dataset.
    % 150 words
    \keywords{Interpretable machine learning \and Local surrogate model}
  \end{abstract}
\fi

>>>>

\ifnum\mode=0
  \pagestyle{plain}
  \pagenumbering{roman}
  \tableofcontents
  \newpage
  \listoffigures\listoftables\clearpage
  \AddToHook{cmd/section/before}{\clearpage}
  \pagestyle{plain}
  \pagenumbering{arabic}
\else
  % The abstract should briefly summarize the contents of the paper in
  % 150--250 words.
  \begin{abstract}
    In recent years,
    complex machine learning models have been introduced
    in various industrial fields due to their high accuracy.
    However,
    their complexity has been a major obstacle to implementation
    in sensitive decision-making situations.
    In order to address this problem,
    various post-hoc explanation methods have been proposed,
    but they have not been able to achieve interpretability of
    both the explanation and its scope.
    We propose a new method, R-LIME,
    which interprets a complex classifier in an interpretable scope.
    R-LIME locally approximates a decision boundary of a black-box classifier
    in a rectangular region
    and maximizes the region as long as the accuracy of the linear
    classifier exceeds a given threshold.
    The resulting rectangular region is interpretable for users because it is
    expressed as a conjunction of feature predicates.
    Through qualitative and quantitative comparisons with the existing method
    on a real-world dataset,
    we demonstrate that R-LIME provides more reliable and interpretable
    explanations than existing methods.
    % 150 words
    \keywords{Interpretable machine learning \and Local surrogate model}
  \end{abstract}
\fi
